Article Title

### 2024-01-05 paper/sn-article-template/sn-article.tex
latex file added

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}

\linespread{1.5} % You can adjust the factor (e.g., 1.5 for 1.5x spacing)

\title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
\author{Your Name}
\date{}

@@

@@

\begin{abstract}
In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids. Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions. The investigation covered diverse operational parameters, including heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number, to quantify the convective heat transfer coefficient. These operational parameters were incorporated as inputs into an artificial neural network to model the convective heat transfer coefficient. Evaluation metrics, such as mean square error and correlation coefficient, were computed, revealing the remarkable performance of the neural network in capturing the underlying processes. The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes. The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
\end{abstract}

@@

While experimental studies provide valuable insights, more research is needed to model the intricate processes and establish empirical relations between effective parameters. Artificial neural networks (ANNs) have proven effective in modeling various processes. For instance, Santra et al. applied ANN to predict heat transfer in laminar natural convection of copper–water nanofluids, demonstrating accurate predictions within the training data range \cite{ref3}. Fazeli et al. utilized ANN to simulate the heat transfer characteristics of a miniature heat sink cooled by SiO2–water nanofluids, achieving excellent agreement with mathematical simulations \cite{ref4}. Balcilar et al. employed ANNs to determine parameters' effects on the heat transfer coefficient of nanofluids, showing good agreement with experimental data \cite{ref5}.

@@

\section{Experimental Setup}
Spherical titanium dioxide nanoparticles dispersed in distilled water and ethylene glycol/water mixture (60 weight-\% ethylene glycol) were used. Nanoparticles were purchased from Degussa (Germany) with an average diameter of 25 nm. An ultrasonic vibrator (Tecna 6) was used for the preparation of mixed aqueous suspensions. The suspension was sonicated for 4 hours at a frequency of 50-60 kHz with an output power of 138W, at 65ºC, and pH=11 by NaOH solution. Nanofluids containing 0.5\%, 1.0\%, 1.5\% titanium dioxide by volume were obtained using the two-step method. The stability time of nanofluids was observed to be 24 hours without any stabilizer.

@@

\begin{equation}
q = h \cdot (T_w - T_f) \quad \text{(2)}
\end{equation}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Learning Algorithm} & \textbf{Minimum MSE} \\ \hline
		Levenberg–Marquardt (LM)   & 0.0010              \\ \hline
	\end{tabular}
	\caption{Performance comparison of back-propagation learning algorithms.}
	\label{tab:learning_algorithms}
\end{table}

As evident from Table 1, the Levenberg–Marquardt (LM) algorithm exhibited the lowest Mean Squared Error (MSE) of 0.0010, establishing it as the most effective back-propagation learning algorithm.

@@

\begin{table}[htbp]
	\centering
	\caption{Comparison of various back propagation learning algorithms}
	\begin{tabular}{cccc}
		\hline
		R2 & MSE & Function & Back Propagation Algorithm \\
		\hline
		0.9899 & 0.0099 & trainrp & Resilient backpropagation (Rprop) \\
		0.9969 & 0.0031 & traincgf & Fletcher–Reeves conjugate gradient backpropagation \\
		0.9957 & 0.0042 & traincgp & Polak–Ribi´ere conjugate gradient backpropagation \\
		0.9960 & 0.0039 & traincgb & Powell–Beale conjugate gradient backpropagation \\
		0.9990 & 0.0010 & trainlm & Levenberg–Marquardt backpropagation \\
		0.9944 & 0.0112 & trainscg & Scaled conjugate gradient backpropagation \\
		0.9963 & 0.0037 & trainbfg & BFGS quasi-Newton backpropagation \\
		0.9957 & 0.0042 & trainoss & One step secant backpropagation \\
		0.9910 & 0.0089 & traingd & Batch gradient descent \\
		0.7778 & 0.2186 & traingdx & Variable learning rate backpropagation \\
		0.8963 & 0.1061 & traingdm & Batch gradient descent with momentum \\
		\hline
	\end{tabular}
\end{table}

@@

>>>>

%Version 2.1 April 2023
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%======================================================%%
%% to compile with pdflatex/xelatex use pdflatex option %%
%%======================================================%%

%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%Note: the following reference styles support Namedate and Numbered referencing. By default the style follows the most common style. To switch between the options you can add or remove “Numbered” in the optional parenthesis. 
%%The option is available for: sn-basic.bst, sn-vancouver.bst, sn-chicago.bst, sn-mathphys.bst. %

%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
%%\documentclass[default]{sn-jnl}% Default
%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published 
%%%%  by Springer Nature. The guidance has been prepared in partnership with 
%%%%  production teams to conform to Springer Nature technical requirements. 
%%%%  Editorial and presentation requirements differ among journal portfolios and 
%%%%  research disciplines. You may find sections in this template are irrelevant 
%%%%  to your work and are empowered to omit any such section if allowed by the 
%%%%  journal you intend to submit to. The submission guidelines and policies 
%%%%  of the journal take precedence. A detailed User Manual is available in the 
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

%\jyear{2021}%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

@@

\title[Article Title]{Article Title}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}

\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}

\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}

%%================================%%
%% Sample for structured abstract %%
%%================================%%

% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
% 
% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}

\keywords{keyword1, Keyword2, Keyword3, Keyword4}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

@@

@@

While experimental studies provide valuable insights, more research is needed to model the intricate processes and establish empirical relations between effective parameters. Artificial neural networks (ANNs) have proven effective in modeling various processes. For instance, Santra et al. applied ANN to predict heat transfer in laminar natural convection of copper?water nanofluids, demonstrating accurate predictions within the training data range \cite{ref3}. Fazeli et al. utilized ANN to simulate the heat transfer characteristics of a miniature heat sink cooled by SiO2?water nanofluids, achieving excellent agreement with mathematical simulations \cite{ref4}. Balcilar et al. employed ANNs to determine parameters' effects on the heat transfer coefficient of nanofluids, showing good agreement with experimental data \cite{ref5}.

@@

\section{Experimental Setup}
Spherical titanium dioxide nanoparticles dispersed in distilled water and ethylene glycol/water mixture (60 weight-\% ethylene glycol) were used. Nanoparticles were purchased from Degussa (Germany) with an average diameter of 25 nm. An ultrasonic vibrator (Tecna 6) was used for the preparation of mixed aqueous suspensions. The suspension was sonicated for 4 hours at a frequency of 50-60 kHz with an output power of 138W, at 65 C, and pH=11 by NaOH solution. Nanofluids containing 0.5\%, 1.0\%, 1.5\% titanium dioxide by volume were obtained using the two-step method. The stability time of nanofluids was observed to be 24 hours without any stabilizer.

@@

\begin{equation}
	q = h \cdot (T_{3i} - T_f) \quad \text{(2)}
\end{equation}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Learning Algorithm} & \textbf{Minimum MSE} \\ \hline
		Levenberg?Marquardt (LM)   & 0.0010              \\ \hline
	\end{tabular}
	\caption{Performance comparison of back-propagation learning algorithms.}
	\label{tab:learning_algorithms}
\end{table}

As evident from Table 1, the Levenberg?Marquardt (LM) algorithm exhibited the lowest Mean Squared Error (MSE) of 0.0010, establishing it as the most effective back-propagation learning algorithm.

@@

\begin{table}[htbp]
	\centering
	\caption{Comparison of various back propagation learning algorithms}
	\begin{tabular}{cccc}
		\hline
		R2 & MSE & Function & Back Propagation Algorithm \\
		\hline
		0.9899 & 0.0099 & trainrp & Resilient backpropagation (Rprop) \\
		0.9969 & 0.0031 & traincgf & Fletcher?Reeves conjugate gradient backpropagation \\
		0.9957 & 0.0042 & traincgp & Polak?Ribiere conjugate gradient backpropagation \\
		0.9960 & 0.0039 & traincgb & Powell?Beale conjugate gradient backpropagation \\
		0.9990 & 0.0010 & trainlm & Levenberg?Marquardt backpropagation \\
		0.9944 & 0.0112 & trainscg & Scaled conjugate gradient backpropagation \\
		0.9963 & 0.0037 & trainbfg & BFGS quasi-Newton backpropagation \\
		0.9957 & 0.0042 & trainoss & One step secant backpropagation \\
		0.9910 & 0.0089 & traingd & Batch gradient descent \\
		0.7778 & 0.2186 & traingdx & Variable learning rate backpropagation \\
		0.8963 & 0.1061 & traingdm & Batch gradient descent with momentum \\
		\hline
	\end{tabular}
\end{table}

@@

%%===========================================================================================%%
%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
%% system, please include the references within the manuscript file itself. You may do this  %%
%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
%% file, and delete the associated \verb+\bibliography+ commands.                            %%
%%===========================================================================================%%

\bibliography{sn-bibliography}% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl
